%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Basile Nouvellet}
\address{1166 Bijlmerdreef \linebreak 1103 JV Amsterdam, France}
\contacts{+33663220918 \linebreak \href{mailto:basile.nouvellet@ponts.org}{basile.nouvellet@ponts.org}}

\begin{document}

    % Build Header
    \makeheader

    % Github and website
    \begin{tabu}
        to 1\textwidth { X[2,l,p] X[c,p] X[2,r,p] }
        {\small \url{https://github.com/BasileNouvellet}} & \textbf{} & {\small \url{https://basile.nouvellet.com}} \\
    \end{tabu}

    % ================================ EDUCATION =======================================================================
    \begin{cvsection}{Education}

        % ------------------------------------ Ponts -------------------------------------------------------------------
        \begin{cvsubsection}{Master's degree}{Ponts ParisTech}{2016--2020 / \textit{Paris, France}}
            \begin{itemize}
                \item \textbf{Major}: Financial Engineering
                \item \textbf{Minor}: Computer Science
                \item \textbf{Coursework} (GPA: 3.77): Software Development, Corporate Finance, Statistics, Entrepreneurship, Game Theory, Financial Market, Operational Research.
            \end{itemize}
        \end{cvsubsection}

        % ------------------------------------ Lazaristes --------------------------------------------------------------
        \begin{cvsubsection}{Preparatory class}{Lyc\'ee Aux Lazaristes}{2014--2016 / \textit{Lyon, France}}
            Intensive and hard working preparatory class for the \textit{Grandes \'Ecoles d'Ing\'enieur} entrance exam on mathematics, physics and engineering science.
        \end{cvsubsection}

    \end{cvsection}

    % ================================ EMPLOYEMENT =====================================================================
    \begin{cvsection}{Employment}

        % ---------------------------- ING -----------------------------------------------------------------------------
        \begin{cvsubsection}{Blockchain Developer}{ING}{Feb 2019--Aug 2019 / \textit{Amsterdam}}
            Built decentralized bank-grade custody solution for digital assets in ING Innovation Lab.
            \begin{itemize}
                \item Developed RESTful APIs (Elixir / Phoenix \& Python) to manage users crypto wallets
                \item Built web portal from scratch (React) with 2-FA authentication using Yubikeys
                \item Reverse-engineered Yubikeys to use them to multi-sign digital assets transactions (Bitcoin, Ethereum \& ERC-20 token)
                \item Deployed to remote Azure machines \& CentOS based private servers using Docker \& Docker-compose
            \end{itemize}
        \end{cvsubsection}

        % ---------------------------- Adactive ------------------------------------------------------------------------
        \begin{cvsubsection}{Full Stack Developer}{Adactive}{July 2018--Jan 2019 / \textit{Singapore}}
            Built custom Web Apps for malls \& airports touch-enabled screens (with React \& Electron), to offer 3D wayfinding services inside buildings.
            \begin{itemize}
                \item Integrated with APIs (RESTful) such as Google Maps and Singapore Bus Network to display live data
                \item Deployed to AWS S3 servers
                \item Optimized app performance to fit hardware specifications (leveraging Redux pattern, asynchronous code with Sagas)
                \item Built a server for synchronizing advertisement medias on 6 different screens (with Express)
            \end{itemize}
            Followed by 2 months of part-time remote freelancing teaching Adactive new tech team (CTO \& devs) about the stack.
        \end{cvsubsection}

        % ---------------------------- Update You ----------------------------------------------------------------------
        \begin{cvsubsection}{Computer Teacher}{Update You}{Jan 2017--July 2018 / \textit{Paris, France}}
            Teached computer usage and resolve technological issues at my clients home, during missions as a self-entrepreneur in a French tech start-up.
            About 15 missions (\textasciitilde 10 different clients).
        \end{cvsubsection}

        % ---------------------------- Town Hall of Paris --------------------------------------------------------------
        \begin{cvsubsection}{Freelance Full Stack Developer}{Town Hall of Paris}{March--Dec 2017 / \textit{Paris, France}}
            Developed a website for an automatic ID card reader based on computer vision and NLP (natural language processing), in partnership with the Junior Enterprise of my engineering school.
        \end{cvsubsection}

    \end{cvsection}

    % ================================ SOFTWARE PROJECTS ===============================================================
    \begin{cvsection}{Software Projects}

        % ---------------------------- Personal website ----------------------------------------------------------------
        \hspace{4pt} \textbf{Personal website:} {\small \color{blue} \url{https://basile.nouvellet.com}} ({\small for additional information and projects})

        % ---------------------------- Quantmetry ----------------------------------------------------------------------
        \begin{cvsubsection}{Crypto-currency price forecasting}{}{}
            \begin{itemize}
                \item[--] Price forecasting of Bitcoin, Ethereum and other crypto-currencies based on tweets published by influencers on Twitter, using machine learning and data science. In partnership with Quantmetry, a French data consulting firm.
                \item[--] \textit{Python, Scikit-Learn, Pandas}
            \end{itemize}
        \end{cvsubsection}

        % ---------------------------- Harvestr ------------------------------------------------------------------------
        \begin{cvsubsection}{Front End development}{}{}
            \begin{itemize}
                \item[--] Implement multiple users management section in the web app of Harvestr, a French tech start-up.
                \item[--] \textit{HTML, CSS, Typescript, Angular}
            \end{itemize}
        \end{cvsubsection}

        % ---------------------------- BCG -----------------------------------------------------------------------------
        \begin{cvsubsection}{Automatic slides generator}{}{}
            \begin{itemize}
                \item[--] Generator that automatically convert a Word document into a PowerPoint presentation. In partnership with the Boston Consulting Group.
                \item[--] \textit{Python, XML}
            \end{itemize}
        \end{cvsubsection}

    \end{cvsection}

    % ================================ ADDITIONAL EXPERIENCE & AWARDS ==================================================
    \begin{cvsection}{Additional Experience and Awards}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}

                % ---------------------------- Une Nuit pour Entreprendre ----------------------------------------------
                \item \textbf{First Prize, Une Nuit pour Entreprendre 2017:} Member of the winning team of \textit{Une Nuit pour Entreprendre} at Ponts ParisTech, a sleepless
                night competition where we created a start-up and pitched it in front of a jury in the morning.
                Coached and challenged by entrepreneurs and professionals.
                Our start-up was about a geolocalized public urban lightning.

            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

    % ================================ SKILLS ==========================================================================
    \begin{cvsection}{Skills}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}
                \item \textbf{Languages:} French (\textit{mother tongue}), English (\textit{fluent}), Spanish (\textit{intermediate})
                \item \textbf{Software:} (\textit{proficient}:) Elixir (OTP), JavaScript, HTML, CSS, React, Node, Python (\textit{familiar}:) Typescript, Angular
                \item \textbf{Technologies:} Git, Electron, Jest, Enzyme, CircleCI, Pandas, Scikit-Learn, Phoenix, Ecto, LESS, Express, PostgreSQL
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

\end{document}
